\documentclass{ExpressiveResume}
\usepackage{amsmath}
\usepackage{comment}
\begin{document}

\resumeheader[
    firstname=Vijay Murari,
    middleinitial=,
    lastname=Tiyyala,
    email=ml.engg.vijay@gmail.com,
    phone=+12405711678,
    linkedin=vijaymuraritiyyala,
    website=imvijay23.github.io,
    state=Bay Area,
]

\section{Summary}
\summary{Machine Learning Engineer with over 2 years of experience in developing and deploying machine learning models.}

\section{Education}
\education{Johns Hopkins University, \textcolor{gray}{\small Baltimore}}{Master's in Computer Science}{Graduated}{Dec 2023}{
    \noindent Focus: Machine Learning, Data Science, NLP, Databases, Information Retrieval, Statistics 
}

\education{VR Siddhartha Engineering College, \textcolor{gray}{\small India}}{Bachelor of Technology in Computer Science}{Graduated}{Jun 2021}{
}
\vspace{7pt}
\section{Technical Skills}

\begin{itemize}
\item Programming Languages: Python, Java, R, C++, C
\item Frameworks and Libraries: PyTorch, TensorFlow, Keras, Langchain, HuggingFace, Deepspeed, Scikit-learn, MLflow 
\item Tools and Platforms: Docker, AWS, Azure, GCP, Git, Kubernetes, PowerBI, Airflow, Weights \& Biases
\item Data Management: SQL, NoSQL, PostgreSQL, Apache Solr, Apache Spark, Hadoop, Elasticsearch
\item Misc: HTML/CSS, PHP, Linux, Shell Scripting, Distributed Computing, CI/CD
\end{itemize}

\section{Work Experience}
\experience{\hyperlink{https://www.clsp.jhu.edu/}{Center for Language and Speech Processing, \textcolor{gray}{\small Full-Time}}}{Machine Learning Engineer}{Aug 2023}{Present}{
\achievement{Engineered an \textbf{empathetic medical chatbot} using \textbf{LlaMA3}, boosting response accuracy to \textbf{88.7\%} on a human-annotated test dataset, enhancing patient interaction quality.}
\achievement{Reduced training time by \textbf{50\%} by leveraging \textbf{PyTorch/SLURM} in a \textbf{multi-GPU} environment for efficient \textbf{distributed} training.}
\achievement{Leveraged \textbf{Apache Solr Cloud} for indexing and retrieval of \textbf{2.5TB} of textual data, optimizing compute and access times.}
\achievement{Enhanced model empathy and factuality through \textbf{Direct Preference Optimization (DPO)/RLHF} training.}
\achievement{Facilitated seamless model deployment to \textbf{AWS} using \textbf{Docker}, ensuring scalable and reliable access.}
}

\experience{\hyperlink{https://www.altmanctr.org/}{UC San Diego, \textcolor{gray}{\small}}}{Applied ML Engineer}{Jan 2024}{Present}{
\achievement{Developed \textbf{Adverse AI}, an NLP tool using BERT models to detect adverse events from unstructured text with \textbf{97.5\%} accuracy.}
\achievement{Created \textbf{HIVTrends.org}, a real-time HIV testing trends platform using ML on search query data, achieving an \textbf{Adjusted R² of 0.87} in predicting testing patterns.}
\achievement{Implemented \textbf{Ridge}, \textbf{Lasso}, and \textbf{XGBoost} models to transform search query trends into predictive HIV testing trends.}
\achievement{Validated the robustness of \textbf{predictive models} by detecting anomalies in predicted sales data, achieving a \textbf{70\%} accuracy.}
\achievement{Enhanced public health surveillance by applying NLP techniques to identify critical safety signals in news articles and social media.}
}

\experience{\hyperlink{https://www.botdojo.com/}{BotDojo, \textcolor{gray}{\small Full-Time}}}{AI Engineer}{Mar 2024}{May 2024}{
\achievement{Developed a \textbf{RAG}-based no-code tool to create \textbf{custom chatbots} using user-uploaded data, enabling seamless API integration.}
\achievement{Focused on the AI component, creating AI evaluations and building individual node components using \textbf{TypeScript} for the frontend.}
\achievement{Collaborated with users to understand their requirements, designed chatbot flows to meet their needs, and resolved any issues.}
\achievement{Integrated chatbots into Teams and Slack, conducting thorough testing to ensure smooth functionality and user experience.}
}

\experience{\hyperlink{https://www.cs.jhu.edu/~mdredze/}{Johns Hopkins University, \textcolor{gray}{\small Full-Time}}}{ML Research Intern}{Jun 2023}{Sep 2023}{
\achievement{Architected a scalable \textbf{RAG} chatbot system for Tobacco Watcher using \textbf{Apache Solr Cloud}, \textbf{FastAPI}, and \textbf{LlaMA2}, capable of handling 100+ concurrent users with 500ms latency.}
\achievement{Implemented a distributed indexing \textbf{ETL} pipeline using \textbf{Apache Spark} to process and index 2M+ of tobacco-related research papers and social media data.}
\achievement{Achieved a \textbf{50\%} reduction in compute costs by using \textbf{PEFT}, \textbf{LoRA}, and \textbf{QLoRA} for efficient \textbf{LlaMA2} training and quantization.}
\achievement{Optimized document retrieval recall to \textbf{90\%} by integrating re-ranking and chunk summarization, optimizing search result relevance.}
\achievement{Managed end-to-end chatbot deployment using \textbf{Docker} and \textbf{FastAPI}.}
}

\experience{\hyperlink{https://www.clsp.jhu.edu/}{Johns Hopkins University, \textcolor{gray}{\small Part-Time}}}{NLP Research Engineer}{Jan 2023}{Jun 2023}{
\achievement{Improved machine translation accuracy to \textbf{86\%} for medical terminologies in low-resource languages, improving accessibility.}
\achievement{Analyzed \textbf{15,000+} compound words, creating a model to improve English translations.}
\achievement{Designed a \textbf{300+} language translation pipeline, enhancing term reconstruction with compound splitting algorithms.}
}

\experience{Deloitte USI, \textcolor{gray}{\small Full-Time}}{Business Technology Analyst}{Jul 2021}{Jun 2022}{
\achievement{Developed stored procedures and scripts for integrating clients' tax data via APIs, and visualized analytical insights in \textbf{PowerBI}.}
\achievement{Accomplished a \textbf{20\%} reduction in tax data processing time by refining \textbf{SQL} procedures for optimization.}
\achievement{Boosted client retention by \textbf{30\%} through improved analytics and reporting, by collaborating with various teams in analyzing and deploying data solutions.}
}

\section{Publications}
\begin{enumerate}
    \item \textbf{Kreyòl-MT: Building MT for Latin American, Caribbean, and Colonial African Creole Languages}, \textit{NAACL 2024}.
    \item \textbf{ANALOBENCH: Benchmarking the Identification of Abstract and Long-context Analogies}, submitted to \textit{ACL 2024}.
\end{enumerate}

\section{Projects}

\project{Python, PyTorch, Git}{Cannabis Use Detection in Clinical EMR}{
\achievement{Trained NLP models such as BERT, RoBERTa, and ClinicalBERT to increase detection accuracy of cannabis use in EHRs by 97\%.}
\achievement{Achieved 92\% accuracy in distinguishing medicinal and recreational cannabis use from unstructured text, enhancing data quality.}
\achievement{Collaborated with clinical researchers to validate model outputs, ensuring compliance with HIPAA and high data fidelity.}
}

\project{Python, PyTorch, Git}{Adverse AI: Automated Discovery of Adverse Event Reports from Unstructured Text}{
\achievement{Led the development of 'Adverse AI', achieving 97.5\% accuracy in identifying adverse events from diverse text sources including medical reports and social media.}
\achievement{Automated extraction and analysis of adverse event data by training models like BERT and RoBERTa, reducing manual review time by 90\%.}
\achievement{Open-sourced the tool to enable widespread adoption and continuous improvement by the healthcare community.}
}

\project{Python, PyTorch, Git}{HIVTrends.org: Real-Time HIV Testing Trends from Search Query Surveillance}{
\achievement{Developed a real-time HIV testing trends platform using search query data, achieving an \textbf{Adjusted R² of 0.87} in predicting testing patterns.}
\achievement{Engineered data pipelines to preprocess and align search query data with HIV testing kit sales, enhancing model training efficiency.}
\achievement{Implemented \textbf{Ridge}, \textbf{Lasso}, and \textbf{XGBoost} models to accurately predict HIV testing trends, improving public health surveillance.}
\achievement{Validated model predictions with anomaly detection, correlating spikes with major HIV awareness events, thereby improving predictive reliability.}
}


\project{Python, PyTorch, HuggingFace, Git, Flask, HTML/CSS, JavaScript}{SAMOYEDS}{
\achievement{Led the design and development of the SAMOYEDS application, a policy simulation tool using LLMs focusing on public health.}
\achievement{Enabled SAMOYEDS to simulate diverse human personas, predicting public health policy responses with \textbf{76\% accuracy}, enhancing policymaker decision-making.}
}

\project{Python, PyTorch, TorchAudio, TorchText, Colab}{Benoit: Better English Noisy Audio Transcripts}{
\achievement{Developed a grammar-correcting ASR model for non-native English speaker audio.}
\achievement{Created synthetic dataset by back-translating English sentences from a low-resource language and passing them to Microsoft SAPI5 TTS to create a proxy for non-native English audio.}
\achievement{Used a GRU-based seq2seq denoising autoencoder on top of a pre-trained Wav2Vec 2.0 (frozen) for grammatically correct ASR.}
}

\project{Python, PyTorch, HuggingFace, Git, HTML/CSS, JavaScript}{ResearchNavigator}{
\achievement{Created an AI information retrieval system/search engine with an interface for research papers, utilized \textbf{LDA} for clustering, and LLMs to generate summaries.}
}

\project{Python, PyTorch, HuggingFace, BeautifulSoup, Git, SLURM}{Code Editing via Natural Language Instructions}{
\achievement{Improved code editing by Instruction-tuning \textbf{CodeLlama2}, achieving a \textbf{37\% pass@1 accuracy} in interpreting natural language instructions, significantly streamlining the coding workflow.}
}

\end{document}
