\documentclass{ExpressiveResume}
\usepackage{amsmath}
\usepackage{comment}
\begin{document}

\resumeheader[
    firstname=Vijay Murari,
    middleinitial=,
    lastname=Tiyyala,
    email=mleng.nlp@gmail.com,
    phone=+12405711678,
    linkedin=vijaymuraritiyyala,
    website=imvijay23.github.io,
    state=Baltimore, MD,
]
\section{Education}
\education{Johns Hopkins University, \textcolor{gray}{\small Baltimore}}{Master's in Computer Science}{Graduated}{Dec 2023}{
    \noindent Focus: Machine Learning, Data Science, NLP, Databases, Information Retrieval, Statistics 
}

\education{VR Siddhartha Engineering College, \textcolor{gray}{\small India}}{Bachelor of Technology in Computer Science}{Graduated}{Jun 2021}{
}
\vspace{7pt}
\section{Technical Skills}

\begin{itemize}
\item Programming Languages: Python, Java, R, C++, C
\item Frameworks and Libraries: PyTorch, TensorFlow, Keras, Langchain, W\&B, HuggingFace, Deepspeed, Scikit-learn, MLflow 
\item Tools and Platforms: Docker, AWS, Azure, GCP, Git, Kubernetes, PowerBI, Airflow
\item Data Management: SQL, NoSQL, PostgreSQL, Apache Solr, Apache Spark, Hadoop, Elasticsearch
\item Misc: HTML/CSS, PHP, Linux, Shell Scripting, Distributed Computing, CI/CD
\end{itemize}


\section{Work Experience}
\experience{\hyperlink{https://www.clsp.jhu.edu/}{Johns Hopkins University, \textcolor{gray}{\small Full-Time}}}{ML Researcher}{Aug 2023}{Present}{
\achievement{Engineered an empathetic medical chatbot using \textbf{LlaMA2}, boosting response accuracy to \textbf{88.7\%} on a human-annotated test dataset, enhancing patient interaction quality.}
\achievement{Reduced training time by \textbf{50\%} by leveraging \textbf{PyTorch/SLURM} in a multi-GPU environment for efficient distributed training.}
\achievement{Leveraged \textbf{Apache Solr Cloud} for indexing and retrieval of \textbf{2.5TB} of textual data, optimizing compute and access times.}
\achievement{Enhanced model empathy and factuality through \textbf{Direct Preference Optimization (DPO)/RLHF} training.}
\achievement{Facilitated seamless model deployment to \textbf{AWS} using \textbf{Docker}, ensuring scalable and reliable access.}
}
\experience{\hyperlink{https://www.clsp.jhu.edu/}{Center for Language and Speech Processing, \textcolor{gray}{\small Full-Time}}}{ML Research Intern}{Jun 2023}{Sep 2023}{
\achievement{Led \textbf{RAG} chatbot development \& integration with \textbf{Apache Solr Cloud} to achieve rapid data indexing and retrieval, significantly reducing user search time by \textbf{70\%}, and boosting web traffic by \textbf{40\%}.}
\achievement{Achieved a \textbf{50\%} reduction in compute costs by using \textbf{PEFT}, \textbf{LoRA}, and \textbf{QLoRA} for efficient \textbf{LlaMA2} training and quantization.}
\achievement{Optimized document retrieval recall to \textbf{90\%} by integrating re-ranking and chunk summarization, optimizing search result relevance.}
\achievement{Managed end-to-end chatbot deployment using \textbf{Docker} and \textbf{FastAPI}.}
}

\experience{\hyperlink{https://www.clsp.jhu.edu/}{Johns Hopkins University, \textcolor{gray}{\small Part-Time}}}{Graduate Research Assistant}{Jan 2023}{Jun 2023}{
\achievement{Improved machine translation accuracy to \textbf{86\%} for medical terminologies in low-resource languages, improving accessibility.}
\achievement{Analyzed \textbf{15,000+} compound words, creating a model to improve English translations.}
\achievement{Designed a \textbf{300+} language translation pipeline, enhancing term reconstruction with compound splitting algorithms.}
}

\experience{Deloitte USI, \textcolor{gray}{\small Full-Time}}{Business Technology Analyst}{Jul 2021}{Jun 2022}{
\achievement{Developed stored procedures and scripts for integrating clients' tax data via APIs, and visualized analytical insights in \textbf{PowerBI}.}
\achievement{Accomplished a \textbf{20\%} reduction in tax data processing time by refining \textbf{SQL} procedures for optimization.}
\achievement{Boosted client retention by \textbf{30\%} through improved analytics and reporting, by collaborating with various teams in analyzing and deploying data solutions.}
}

\section{Projects}


\project{Python, PyTorch, SciPy, Git}{ECGNet: ECG Signal Processing and Arrhythmia Classification System}{
\achievement{Developed ECGNet, leveraging deep learning to achieve high accuracy in detecting and classifying arrhythmias from ECG signals.}
\achievement{Implemented data augmentation and signal processing techniques to enhance model training on diverse ECG datasets.}
\achievement{Utilized PyTorch for model development, focusing on CNNs and RNNs to capture complex signal patterns.}

}

\project{Python, PyTorch, HuggingFace, Git, Flask}{ResearchNavigator: AI-Powered Research Paper Search Engine}{
\achievement{Created an AI search engine to facilitate efficient access to research papers, enhancing academic and clinical research.}
\achievement{Employed LDA for clustering and LLMs to generate concise, informative summaries of research papers.}
}
\project{Python, PyTorch, Databricks, MLflow}{Personalized Treatment Recommendation System}{
\achievement{Developed and deployed a NLP-based recommendation system in Databricks, enhancing patient adherence by 20\%.}
}

\project{Python, Scikit-learn, K-Means, Hierarchical Clustering, Dash}{Patient Engagement and Retention Analysis}{
\achievement{Streamlined patient engagement with a Dash app by segmenting adherence patterns using K-Means and Hierarchical Clustering.}
}



\section{Publications}
\project{Awaiting Decision}{NAACL 2024 [1], ACL 2024 [1]}{}
\end{document}
