\documentclass{ExpressiveResume}
\usepackage{amsmath}
\usepackage{comment}
\begin{document}

\resumeheader[
    firstname=Vijay Murari,
    middleinitial=,
    lastname=Tiyyala
]

\begin{comment}
Cover Letter for Click Therapeutics Machine Learning Engineer Position
\end{comment}

\opening{Dear Hiring Team at Click Therapeutics,}

I am writing to express my keen interest in the Machine Learning Engineer position at Click Therapeutics. With a Master's degree in Computer Science from Johns Hopkins University and extensive experience in machine learning, data science, and software development, I am excited about the opportunity to contribute to your team's efforts in developing groundbreaking digital therapeutics.

At Johns Hopkins University and in my professional engagements, I have focused on leveraging machine learning and artificial intelligence to solve complex problems in healthcare and related fields. My work includes developing an empathetic medical chatbot, enhancing patient interaction quality, and creating efficient distributed training systems for large-scale data analysis. These projects have not only honed my technical skills in Python, PyTorch, TensorFlow, and AWS but also instilled a deep understanding of the importance of data security, user privacy, and patient-centric design in healthcare applications.

I am particularly drawn to Click Therapeutics' commitment to delivering clinically proven, FDA-regulated digital treatments that address unmet medical needs. The interdisciplinary approach of combining cognitive, behavioral, and neuromodulatory mechanisms with advanced data-driven tools like AI and machine learning resonates with my professional experience and personal interests.

My background in developing algorithms for mental health classification, disease state forecasting, and implementing features to increase product engagement aligns well with the key challenges outlined for this role. I am also excited about the prospect of working in a hybrid environment from your offices in Tribeca, NYC, or Boston, MA, and contributing to the vibrant digital health community there.

I am eager to bring my expertise in machine learning infrastructure, model development, and deployment to Click Therapeutics. I look forward to the possibility of discussing how my skills, experience, and passion for digital health innovation can support your mission to provide patients with access to effective digital therapeutics.

Thank you for considering my application. I am looking forward to the opportunity to discuss how I can contribute to the success of Click Therapeutics.

\closing{Sincerely,}

\signature{Vijay Murari Tiyyala}

\end{document}
